OptiFit: an improved method for fitting amplicon sequences to existing OTUs

### 2021-12-15 paper/paper_before-review.Rmd
Rename manuscript version from before review

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE}
schtools::set_knitr_opts()
knitr::opts_knit$set(base.dir = here::here(),
                     base.url = "../")
knitr::opts_chunk$set(fig.path = 'figures/',
                      dpi = 300)
```

>>>>

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE}
schtools::set_knitr_opts()
#knitr::opts_knit$set(base.dir = here::here(),
#                     base.url = "../")
knitr::opts_chunk$set(fig.path = 'figures/',
                      dpi = 300)
```
